Reinforcement Learning Based Transmitter-Receiver Selection for Distributed MIMO Radars

### 2020-01-21 paper.tex
IMPROVE readability

A well-known framework, called multi-armed bandits (MAB) framework, provides policies for selecting actions to balance the exploration and exploitation trade-off while maximizing the employed reward function \cite{Lattimore2019}
In the literature, such a framework is effectively used, for example, for opportunistic spectrum access, where the secondary user must select the frequency band without interfering with the primary user \cite{Zhao2008}.
In addition, authors in \cite{Mukherjee2012} and \cite{Kuai2019} propose using a combinatorial MAB approach as a robust way for selecting the MIMO antenna subset for maximizing throughput in communication systems.
Extensions from combinatorial multi-armed bandits are used to address the problem with exponentially growing action space in the function of antennas.

@@

Usually in the combinatorial MAB problem, the agent does not know the mapping from the arm rewards to the super arm rewards.
However, here the reward function $\eqref{eq:reward_func}$ is known which enables us to use MAB algorithms from the classical MAB problem.
Similar approach is used for MIMO antenna subset selection in mobile communications, where each arm represents power-normalized throughput for each antenna and UCB1-algorithm paired with an exhaustive search were used to solve the subset selection problem \cite{Mukherjee2012}.
The reward distributions were assumed stationary in \cite{Mukherjee2012}.

In this paper we generalize the approach in \cite{Mukherjee2012} to any index-based algorithm and non-stationary reward distributions. 
The proposed algorithm for solving the combinatorial MAB problem with known mapping from the arm rewards to the super arm rewards is shown in Algorithm~\ref{alg:gcmab}.
On line~\ref{alg:calc_idx} of the Algorithm~\ref{alg:gcmab} any index-based MAB algorithm can be used to find the indexes, and on line~\ref{alg:find_sa} any optimization method can be used to find the super arm.
The indexes calculated by a MAB algorithm will ensure that the exploration and exploitation trade-off is balanced well.

>>>>

A multi-armed bandit (MAB) framework, provides policies for selecting actions to balance the exploration and exploitation trade-off while maximizing the employed reward function \cite{Lattimore2019}.
In the literature, such a framework is effectively used for example in opportunistic spectrum access, in which the secondary user must choose frequency band in a way that interference to the primary user is not caused \cite{Zhao2008}.
Also, authors in \cite{Mukherjee2012} and \cite{Kuai2019} propose using a combinatorial MAB approach as a robust way for selecting the MIMO antenna subset for maximizing throughput in communication systems.
Extensions from combinatorial multi-armed bandits are used to address the problem with large combinatorial action space.

@@

Usually in the combinatorial MAB problem, the agent does not know the mapping from the arm rewards to the super arm rewards.
However, here the reward function $\eqref{eq:reward_func}$ is known which enables us to use MAB algorithms from the classical MAB problem.
Authors in \cite{Mukherjee2012} and \cite{Kuai2019} use similar approach for MIMO antenna selection in mobile communications to maximize the throughput.
The approach in \cite{Mukherjee2012} use UCB-1 algorithm and the reward statistics are constant.
While, authors in \cite{Kuai2019} use Thompson sampling and non-stationary and stationary rewards are considered.

In this paper we generalize the approaches in \cite{Mukherjee2012, Kuai2019} to any index-based algorithm and non-stationary reward distributions. 
The proposed algorithm for solving the combinatorial MAB problem with known mapping from the arm rewards to the super arm rewards is shown in Algorithm~\ref{alg:gcmab}.
On line~\ref{alg:calc_idx} of the Algorithm~\ref{alg:gcmab} any index-based MAB algorithm can be used to find the indexes, and on line~\ref{alg:find_sa} any optimization method can be used to find the super arm.
The indexes calculated by a MAB algorithm will ensure that the exploration and exploitation trade-off is balanced well.
